---
title: "Tidyquant Demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyquant)
```

Tutorial from http://www.business-science.io/code-tools/2017/10/23/demo_week_tidyquant.html

# Stock Prices 

## Get Stock price data

```{r}
# Get Stock Prices from Yahoo! Finance

FANG_symbols <- c("FB", "AMZN", "NFLX", "GOOG")

# daily stock prices
FANG_data_d <- FANG_symbols %>%
    tq_get(get = "stock.prices", 
           from = "2014-01-01", 
           to = "2016-12-31")

FANG_data_d
```

## Simple Stock price plot .. 

```{r}
FANG_data_d %>%
    ggplot(aes(x = date, y = adjusted, color = symbol)) + 
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    theme_tq() +
    scale_color_tq()
```


# Economic Data

Data from FRED : https://fred.stlouisfed.org/

```{r}
# Economic Data from the FRED

# Create a vector of FRED symbols
FRED_symbols <- c('ETOTALUSQ176N',    # All housing units
                  'EVACANTUSQ176N',   # Vacant
                  'EYRVACUSQ176N',    # Year-round vacant
                  'ERENTUSQ176N'      # Vacant for rent
)

# Pass symbols to tq_get to get economic data
FRED_data_m <- FRED_symbols %>%
    tq_get(get="economic.data", 
           from = "2001-04-01")

# Show results
FRED_data_m
```

## Economic Data Plotting

Daily data

```{r}

FRED_data_m %>%
    ggplot(aes(x = date, y = price, color = symbol)) + 
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    theme_tq() +
    scale_color_tq() +
    labs(title = "Visualize Economic Data")
```

# Mutating Data

Change periodicity from daily to monthly using to.period from xts

```{r}
FANG_data_m <- FANG_data_d %>%
    group_by(symbol) %>%
    tq_transmute(
        select      = adjusted,
        mutate_fun  = to.period,
        period      = "months"
    )

FANG_data_m
```

## Transmute / Transformation

Before Transform

```{r}
# Daily data
FANG_data_d %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    scale_color_tq() +
    theme_tq() +
    labs(title = "Before transformation: Too Much Data")
```

After Transform

```{r}
# Monthly data
FANG_data_m %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_point() +
    geom_line() +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    scale_color_tq() +
    theme_tq() +
    labs(title = "After transformation: Easier to Understand")
```

## Lags

Lags - Get first 5 lags

```{r}

# Pro Tip: Make the new column names first, then add to the `col_rename` arg
column_names <- paste0("lag", 1:5)

# First five lags are output for each group of symbols
FANG_data_d %>%
    select(symbol, date, adjusted) %>%
    group_by(symbol) %>%
    tq_mutate(
        select     = adjusted,
        mutate_fun = lag.xts,
        k          = 1:5,
        col_rename = column_names
    )
```


## Rolling Functions

30 and 90 day rolling averages

```{r}
FANG_data_d_avgs <- FANG_data_d %>%
    select(symbol, date, adjusted) %>%
    group_by(symbol) %>%
    tq_mutate(
        select     = adjusted,
        mutate_fun = rollapply,
        width      = 30,
        FUN        = mean,
        na.rm      = TRUE,
        col_rename = "mean_roll_30"
    ) %>%
  tq_mutate(
        select     = adjusted,
        mutate_fun = rollapply,
        width      = 90,
        FUN        = mean,
        na.rm      = TRUE,
        col_rename = "mean_roll_90"
    ) %>%
  tq_mutate(
        select     = adjusted,
        mutate_fun = rollapply,
        width      = 180,
        FUN        = mean,
        na.rm      = TRUE,
        col_rename = "mean_roll_180"
    ) %>%
  tq_mutate(
        select     = adjusted,
        mutate_fun = rollapply,
        width      = 270,
        FUN        = mean,
        na.rm      = TRUE,
        col_rename = "mean_roll_270"
    )


FANG_data_m_avgs <- FANG_data_d_avgs %>%
    group_by(symbol) %>%
    tq_transmute(select = c("adjusted", "mean_roll_30", "mean_roll_90", "mean_roll_180", "mean_roll_270"), 
                 mutate_fun = to.period, 
                 period = "months")
```



```{r}
# Daily data
FANG_data_m_avgs %>%
    ggplot(aes(date,adjusted,color = symbol)) +
    geom_point() +
    geom_line() +
    geom_line(aes(y = mean_roll_30), color = 'green') +
    geom_line(aes(y = mean_roll_90), color = 'red') +
    geom_line(aes(y = mean_roll_180), color = 'blue') +
    geom_line(aes(y = mean_roll_270), color = 'yellow') +
    facet_wrap(~ symbol, ncol = 2, scales = "free_y") +
    scale_color_tq() +
    theme_tq()
```






```{r}
# Rolling quantile
FANG_data_d %>%
    select(symbol, date, adjusted) %>%
    group_by(symbol) %>%
    tq_mutate(
        select     = adjusted,
        mutate_fun = rollapply,
        width      = 5,
        by.column  = FALSE,
        FUN        = quantile,
        probs      = c(0, 0.025, 0.25, 0.5, 0.75, 0.975, 1),
        na.rm      = TRUE
    )
```

## Other Functions 

```{r}
tq_transmute_fun_options()
```

